Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1130

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------
\section{Introduction}
\subsection{Model}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb{R}^d),
\end{equation}
    where $\sigma>0$ and $b>0$.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta},
    \quad z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0$ and $\beta \in (0,1) $.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite measures on $\mathbb{R}^d$.
    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
    Put $\|\mu\|=\langle 1,\mu\rangle$ if it is well defined.
    We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

@@

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
\added{
    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
$
	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
$
and
$
	Q f:= Q_{\kappa_f}f.
$
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
}
	\deleted{
	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by 
	     \mathcal{P}_{\kappa}
    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
	Then
	\begin{itemize}
	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.

	\end{itemize}
	}
\subsection{}
    Let $X$ be the super OU-process discussed in the first subsection.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

@@

\section{Preliminaries}
    In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
$
   	\mathcal I_a^b Y
    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
$
	Then we have an nature incremental decomposition of $Y$:
\begin{align}
    \mathcal I_0^t Y
    = \sum_{k = 0}^{\lfloor t \rfloor - 1} \mathcal I_k^{k+1}Y + \mathcal I_{\lfloor t \rfloor}^t Y,
    \quad t\geq 0.
\end{align}
	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
\deleted{	
	In this case we have
\begin{align}
    I_a^b[\langle g,X_t\rangle]
    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
\end{align}
}

    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
\deleted{
    The first reason for considering $\gamma$-controllable operators is the following:
\begin{lem}
    Suppose that operators $(A_\lambda)_{\lambda\in \Lambda}$ are uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$.
    Then \added{for each $\kappa\geq0$,} there exists a $\gamma$-scalable operator $S$ such that
\[
    |A_\lambda T_t^\alpha f|
    \leq e^{\gamma t (\alpha  - \added{\kappa} b)} S\added{Q_{\kappa}}f,
    \quad \lambda \in \Lambda, t\geq 0, f\in \added{ \mathcal{D}\cap\mathcal{P}_{\kappa}}.
\]
\end{lem}

>>>>

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {CLT for Super-OU Processes with stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------
\begin{abstract}
    Consider a super-OU process $\{X_t, t\geq 0\}$ with branching mechanism $\psi(z)=-\alpha z +z^{1+\beta}$, where $\alpha >0$ and $\beta\in (0,1)$. For each testing function $f$ with polynomial growth, denote by $\kappa_f$ the order of $f$ in term of the spectral decomposition of $f$ with respect to the mean semigroup of $X$. Conditioned on no-extinction, we establish some spatial central limit theorem for $\langle f, X_t \rangle$ under three different regimes: In the small branching case, $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{+\beta}}$ convergences weakly. In the critical branching case, $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{+\beta}}$ convergences weakly. In the large branching case,  $\alpha\beta> \kappa_f b(1+\beta)$, $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ convergences a.s and in $L^{1+\gamma}$, with $\gamma \in (0,\beta)$.
\end{abstract}
\section{Introduction}
\subsection{Model}
    Let $d \in \mathbb N:= \{1,2,\dots\}$ and
    %\deleted{For each $x\in \mathbb{R}^d$, write $|x|$ for its Euclidean norm.}
    $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with infinitesimal generator $L$ such that
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb{R}^d),
\end{equation}
    where $\sigma>0$ and $b>0$.
    Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with
\begin{equation}\label{mechanism}
    \psi(z)
    := - \alpha z + z^{1+\beta},
    \quad z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0$ and $\beta \in (0,1) $.
    Denote by $\mathcal{M}(\mathbb{R}^d)$ the space of all finite measures on $\mathbb{R}^d$.
    For each measurable function $f$ and measure $\mu$ write $\langle f,\mu\rangle = \int f(x)\mu(dx)$.
    Put $\|\mu\|=\langle 1,\mu\rangle$ if it is well defined.
    We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}

@@

\subsection{OU semigroup}
    In this subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}.
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    \varphi(x)dx
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h  \in \mathcal B(\mathbb R^d, \mathbb R): \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
     Let $\mathbb N = \{1,2,\dots\}$ and $\mathbb N_0 := \mathbb N\cup\{0\}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p| \added{ :}=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k !$ and $\partial x^p:= \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that $(T_t)$ is a strong continuous semigroup on $L^2(\varphi)$ and its generator $L$ has eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    For each $k \in \mathbb N_0$, denote $A_k$ the eigenspace corresponding to eigenvalue $-bk$, then
\begin{equation}
    A_k
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
    \phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    Moreover, $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
    Denote by
\begin{equation}\label{order}
    \kappa_f
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb N_0^d ,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    the order of function $f$ in $L^2(\varphi)$.
    Note that $ \kappa_f\geq 0$.
    In particular, the order of any constant function is zero.
    Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$ with
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathscr B(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is clear that $\mathcal{P} \subset L^2(\varphi)$.
    For each $\kappa \in \mathbb Z_+$ and $f\in \mathcal P$, define
$
	Q_\kappa f := \sup_{t\geq 0} e^{\kappa b t}|T_t f|,
$
and
$
	Q f:= Q_{\kappa_f}f.
$
    Then according to \cite[Fact 1.2]{MM}, $Q$ is an operator from $\mathcal P$ to $\mathcal P$.
\begin{comment}

	\deleted{
	For each $\kappa\geq0$, define $\mathcal{P}_{\kappa}$ by
	\begin{align}
	     \mathcal{P}_{\kappa}
    :=\big \{f\in \mathcal{P}:\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ \sup_{t\geq0}e^{\kappa b t}|T_tf(x)|\leq C(1+|x|)^n\big\}.
	\end{align}
	and an operator $Q_{\kappa}:\mathcal{P}_{\kappa}\mapsto\mathcal{P}\cap\mathscr{B}(\mathbb{R}^d,\mathbb{R}_+)$ by $Q_{\kappa}f=\sup_{t\geq0}e^{\kappa b t}|T_tf|$.
	Then
	\begin{itemize}
	    \item For each $\kappa_1\geq \kappa_2$, $\mathcal{P}_{\kappa_1}\subset\mathcal{P}_{\kappa_2}$, and $\mathcal{P}=\cup_{\kappa\geq 0}\mathcal{P}_{\kappa}$.
	    \item for each $f\in \mathcal{P}$, then $f\in \mathcal{P}_{\kappa_f}$, and $Q_{\kappa}f\leq Qf:=Q_{\kappa_f}f$, $\kappa\leq \kappa_f$.

	\end{itemize}
	}
\end{comment}
\subsection{}
    Let $X$ be the super OU-process discussed in the first subsection.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathcal B(\mathbb R^d, \mathbb C_+)$ and $x\in \mathbb R^d$, define $\Psi_0f(x) := \psi_0(f(x))$ and $\Psi'_0 f(x) := \psi'_0(f(x))$.
    For each $t\in [0,\infty), x\in \mathbb R^d $ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

@@

\section{Preliminaries}
    In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
	For each $0 \leq a \leq b <\infty$ and  random variable $Y$ with finite mean, define random variable
$
   	\mathcal I_a^b Y
    := \mathbb P[Y|\mathscr F_b] - \mathbb P[Y|\mathscr F_a].
$
	Then we have an nature incremental decomposition of $Y$:
\begin{align}
    \mathcal I_0^t Y
    = \sum_{k = 0}^{\lfloor t \rfloor - 1} \mathcal I_k^{k+1}Y + \mathcal I_{\lfloor t \rfloor}^t Y,
    \quad t\geq 0.
\end{align}
	The random variable we are interested in is $Y:= \langle g,X_t\rangle$.
\begin{comment}

\deleted{	
	In this case we have
\begin{align}
    I_a^b[\langle g,X_t\rangle]
    = I_a^b\big[\mathbb P[\langle g,X_t\rangle|\mathscr F_b]\big]
    = I_a^b[ \langle T_{t-b}^\alpha g, X_b \rangle ].
\end{align}
}
\end{comment}
    Define $\mathcal P^+:= \mathcal P \cap \mathcal B(\mathbb R^d, \mathbb R_+)$ and $\mathcal P^*:= \{f\in \mathscr B(\mathbb R^d, \mathbb C): |f|\in \mathcal P\}$.
    We say $S$ is a $\gamma$-scalable operator for some $\gamma\in \mathbb R$ if $S: \mathcal P^+ \to \mathcal P^+$ and $S(\theta f) = \theta^\gamma Sf$ for each $\theta \geq 0$ and $f \in \mathcal P^+$.
    We say $R$ is a monotonic operator if $R:\mathcal P^+ \to \mathcal P^+$ and $Rf \leq Rg$ for each $f, g \in \mathcal P^+$ with $f\leq g$.
    We say $(R,S)$ is a $\gamma$-control-pair for some $\gamma \in \mathbb R$ if $R$ is a monotonic operator and $S$ is a $\gamma$-scalable operator and $Rf\leq Sf$ for each $f\in \mathcal P^+$.
    We say an operator $A$ is $\gamma$-controllable on $\mathcal D $ for some $\gamma \in \mathbb R$ if $A: \mathcal D \to \mathcal P^*$ and there  is a $\gamma$-control pair $(R,S)$ such that $|Af|\leq R|f|$ for each $f\in \mathcal D$.
    In this case we say $A$ is $\gamma$-controlled by the $\gamma$-control-pair $(R,S)$ on $\mathcal D$.
    We say a family of operator $(A_s)_{s\in \Lambda}$ is uniformly $\gamma$-controllable on $\mathcal D\subset \mathcal P^*$ for some $\gamma \in \mathbb R$ if there is a $\gamma$-control pair $(R,S)$ such that $A_s$ is $\gamma$-controlled by $(R, S)$ on $\mathcal D$, for each $s\in \Lambda$.
    \begin{comment}

\deleted{
    The first reason for considering $\gamma$-controllable operators is the following:
\begin{lem}
    Suppose that operators $(A_\lambda)_{\lambda\in \Lambda}$ are uniformly $\gamma$-controllable on $\mathcal D$ for some $\gamma \in \mathbb R$ and $\mathcal D \subset \mathcal P^*$.
    Then \added{for each $\kappa\geq0$,} there exists a $\gamma$-scalable operator $S$ such that
\[
    |A_\lambda T_t^\alpha f|
    \leq e^{\gamma t (\alpha  - \added{\kappa} b)} S\added{Q_{\kappa}}f,
    \quad \lambda \in \Lambda, t\geq 0, f\in \added{ \mathcal{D}\cap\mathcal{P}_{\kappa}}.
\]
\end{lem}

\begin{proof}
    Let $(R,S)$ be the $\gamma$-control-pair for $(A_\lambda)_{\lambda\in \Lambda}$.
    Then
\[
    |A_\lambda T_t^\alpha f| \leq R|T_t^\alpha f|
    \leq R (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
    \leq S (e^{\alpha t  - \kappa bt}Q_{\kappa}f)
    \leq e^{\gamma t (\alpha  - \kappa b)} SQ_{\kappa}f.
    \qedhere
\]
\end{proof}
}
\end{comment}
	For two operators $A: \mathcal D_A \to \mathcal P^*$ and $B: \mathcal D_B \to \mathcal P^*$, define $(A\times B)f (x):= Af(x) \times Bf(x)$ for each $f\in \mathcal D_A \cap \mathcal D_B$ and $x\in \mathbb R^d$.
    Let $a > 0$, define $A^{\times a}f(x):= (Af(x))^a$ for each $f\in \mathcal D_A$ and $x\in \mathbb R^d$.
    The reason for considering $\gamma$-controllable operators is that they have good algebra properties:
\begin{lem}
\label{lem: property of controllable operators}
    Let operators $(A_\lambda)_{\lambda\in \Lambda}$ be uniformly $\gamma$-controllable on $\mathcal D$ from some $\gamma \in \mathbb R$ and $\mathcal D\subset \mathcal P^*$:
\begin{itemize}
\item[(1)]
    Suppose that $(\Lambda, \mathscr F)$ is a measurable space.
    Also suppose that $(\lambda,x)\mapsto A_\lambda f(x)$ is $\mathscr F \otimes \mathscr B(\mathbb R^d)$-measurable for each $f\in \mathcal D$.
    For each probability measure $\mu$ on $(\Lambda, \mathscr F)$ write
\[
    A_\mu f(x):= \int_{\Lambda} A_\lambda f (x)~\mu(d\lambda), \quad f\in \mathcal D, x\in \mathbb R^d.
\]
    Then operators $\{A_\mu: \mu \text{ is  a probability measure on } (\Lambda, \mathscr F)\}$ are uniformly $\gamma$-controllable on $\mathcal D$.
\item[(2)]
    Suppose that operators $(B_\delta)_{\delta\in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D_0 \subset \mathcal P^*$ for some $\beta \in \mathbb R$.
    Also suppose that for each $\lambda$, $A_\lambda:\mathcal D \to \mathcal D_0$.
    Then operators $(B_\delta A_\lambda)_{\delta\in \Delta, \lambda \in \Lambda}$ is uniformly $(\gamma\beta)$-controllable on $\mathcal D$.
\item[(3)]
    Suppose that operators $(B_\delta)_{\delta \in \Delta}$ is uniformly $\beta$-controllable on $\mathcal D$ for some $\beta\in \mathbb R$.
    Then operators $(B_\delta\times A_\lambda)_{\delta \in \Delta, \lambda \in \Lambda}$ are uniformly $(\gamma+\beta)$-controllable.
\item[(4)]
    Let $a>0$. Suppose that, for each $\lambda \in \Lambda$, $A_\lambda : \mathcal D \to \mathcal P^+$.
    Then operators $(A^{\times a}_\lambda)_{\lambda \in \Lambda}$ are uniformly $(a\gamma)$-controllable.
\end{itemize}
\end{lem}
\begin{proof}
    Proof of (1): Let $(R,S)$ be the $\gamma$-control-pair of $(A_\lambda)_{\lambda\in\Lambda}$ on $\mathcal{D}$. For each $f \in \mathcal{D}$ and $\mu$ the probability measure on $(\Lambda, \mathscr F)$.
\[
   |A_{\mu}f(x)|\leq \int_{\Lambda}|A_{\lambda}f(x)|\mu(d\lambda) \leq \int_{\Lambda}R|f|(x)\mu(d\lambda) \leq R|f|(x).
\]
